---
title: "simpleRegress"
author: "Gil Felix"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

The bears neck is 20 inches around and 57 in length. When looking at the accompanying data, it shows that the residual standard errors is 5.376, and the R-squared is 0.7524. 
 
## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

```{r}
mychest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(mychest)
summary.lm(mychest)
```

The residual standard error is 4.939 and lower than the previous model.In addition, the R-squared is 0.791, which is higher than the previous model, 0.7524, and is also better. In ranking chest is above neck.

```{r}
myhead <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(myhead)
summary.lm(myhead)
```

As the third model, the residual standard error is 7.32, which is making it worse. In addition, the R-squared is now 0.5409 making it a decline from the previous model (my chest). Comparing all three models, this one is at the bottom of the list. Ranking is: chest, then neck, then Head 































